\clearpage
\section*{СПИСОК ИСПОЛЬЗОВАННОЙ ЛИТЕРАТУРЫ (APA)}
\addcontentsline{toc}{section}{СПИСОК ИСПОЛЬЗОВАННОЙ ЛИТЕРАТУРЫ (APA)}

\begingroup
\setlength{\bibhang}{1.25cm}
\setlength{\bibsep}{0.4\baselineskip}
\begin{thebibliography}{99}

\bibitem[Antonova \& Smirnov(2024)]{metrics2024}
Antonova, I. I., \& Smirnov, V. A. (2024). \textit{Statisticheskie metody v upravlenii kachestvom}. Yurait.

\bibitem[Buttle \& Maklan(2022)]{crmBook}
Buttle, F., \& Maklan, S. (2022). \textit{Customer relationship management: Concepts and technologies} (4th ed.). Routledge.

\bibitem[Chistov et~al.(2025)]{isDesign2025}
Chistov, D. V., Melnikov, P. P., Zolotaryuk, A. V., \& Nicheporuk, N. B. (2025). \textit{Proektirovanie informacionnyh sistem: Uchebnik dlya SPO}. Yurait.

\bibitem[Dart Team(2026)]{dartDocs}
Dart Team. (2026). \textit{Dart documentation}. \url{https://dart.dev/guides}

\bibitem[Date(2022)]{dataDesign2022}
Date, C. J. (2022). \textit{Database design and relational theory} (2nd ed.). O'Reilly Media.

\bibitem[Eyal(2021)]{productivityBook}
Eyal, N. (2021). \textit{Hooked: How to build habit-forming products}. Portfolio.

\bibitem[Freeman \& Robson(2021)]{designPatterns}
Freeman, E., \& Robson, E. (2021). \textit{Head first design patterns} (2nd ed.). O'Reilly Media.

\bibitem[Flutter Team(2026a)]{flutterDocs}
Flutter Team. (2026a). \textit{Flutter documentation}. \url{https://docs.flutter.dev}

\bibitem[Flutter Team(2026b)]{goRouterDocs}
Flutter Team. (2026b). \textit{GoRouter package documentation}. \url{https://pub.dev/packages/go_router}

\bibitem[Humble \& Farley(2022)]{softwareEconomics2022}
Humble, J., \& Farley, D. (2022). \textit{Continuous delivery and software economics in practice}. Addison-Wesley.

\bibitem[Kerzner(2022)]{projectManagementBook}
Kerzner, H. (2022). \textit{Project management: A systems approach to planning, scheduling, and controlling}. Wiley.

\bibitem[Krug(2023)]{uxBook2023}
Krug, S. (2023). \textit{Don't make me think, revisited for modern products}. New Riders.

\bibitem[Martin(2021)]{cleanArchitecture}
Martin, R. C. (2021). \textit{Clean architecture: A craftsman's guide to software structure and design}. Prentice Hall.

\bibitem[OWASP Foundation(2021a)]{owaspM1}
OWASP Foundation. (2021a). \textit{OWASP Top 10 2021: Broken access control}. \url{https://owasp.org/Top10/A01_2021-Broken_Access_Control/}

\bibitem[OWASP Foundation(2021b)]{owaspM4}
OWASP Foundation. (2021b). \textit{OWASP Top 10 2021: Insecure design}. \url{https://owasp.org/Top10/A04_2021-Insecure_Design/}

\bibitem[OWASP Foundation(2021c)]{owaspM10}
OWASP Foundation. (2021c). \textit{OWASP Top 10 2021}. \url{https://owasp.org/Top10/}

\bibitem[Pecorelli et~al.(2023)]{testingBook}
Pecorelli, A., et al. (2023). \textit{Testing Flutter applications}. Manning.

\bibitem[PostgreSQL Global Development Group(2025)]{postgresDocs}
PostgreSQL Global Development Group. (2025). \textit{PostgreSQL 16 documentation}. \url{https://www.postgresql.org/docs/16/}

\bibitem[Project Team(2026a)]{repoReadme}
Project Team. (2026a). \textit{Gamified Task CRM (Flutter Web): README and runtime guide}. Internal project documentation.

\bibitem[Project Team(2026b)]{docsIndex}
Project Team. (2026b). \textit{Docs index for current runtime}. Internal project documentation.

\bibitem[Project Team(2026c)]{docsDefenseScript}
Project Team. (2026c). \textit{Defense demo script}. Internal project documentation.

\bibitem[Project Team(2026d)]{migrationClientId}
Project Team. (2026d). \textit{Migration: Add client\_id to public.tasks}. SQL migration document.

\bibitem[Project Team(2026e)]{bootstrapSchema}
Project Team. (2026e). \textit{Bootstrap runtime schema for Supabase}. SQL migration document.

\bibitem[Richards \& Ford(2022)]{patternsBook}
Richards, M., \& Ford, N. (2022). \textit{Fundamentals of software architecture}. O'Reilly Media.

\bibitem[Rousselet(2026)]{riverpodDocs}
Rousselet, R. (2026). \textit{Riverpod documentation}. \url{https://riverpod.dev}

\bibitem[Satzinger et~al.(2023)]{isDesign2023}
Satzinger, J., Jackson, R., \& Burd, S. (2023). \textit{Systems analysis and design in a changing world} (8th ed.). Cengage.

\bibitem[Silberschatz et~al.(2021)]{dbBook2021}
Silberschatz, A., Korth, H., \& Sudarshan, S. (2021). \textit{Database system concepts} (7th ed.). McGraw-Hill.

\bibitem[Sommerville(2022)]{sommerville}
Sommerville, I. (2022). \textit{Software engineering} (11th ed.). Pearson.

\bibitem[Supabase Inc.(2026)]{supabaseDocs}
Supabase Inc. (2026). \textit{Supabase documentation}. \url{https://supabase.com/docs}

\end{thebibliography}
\endgroup
